---
title: "project"
author: "mrthinks@gmail.com"
date: "2015. 11. 22."
output: html_document
---

# Load related library
```{r, echo=FALSE}
library(caret)
library(list)
library(MASS)
```

# Load data
Set invalid data to 'NA'.
```{r}
training <- read.csv("pml-training.csv", stringsAsFactors=FALSE, na.strings = c("NA", ""))
```

# Evaluate input variables.
Set invalid data to 'NA'.
```{r}
training_tf <- ifelse(is.na(training), 1, 0)
training_tf_cml <- colSums(training_tf)
training_tf_cml_nor <- training_tf_cml / dim(training_tf)[1]

hist(training_tf_cml_nor)
```

I select variables, which has more than 90% of data is valid.
```{r}
validColumns <- training_tf_cml_nor < 0.1
training2 <- training[, validColumns]
```

Remove meaningless variable, too.
```{r}
training3 <- training2[,8:60]
dim(training3)
```

# Make balanced data
```{r}
type_list <- unique(training3$classe)
table(training3$classe)
min_sample <- min(table(training3$classe))

training4 <- NULL
for(str in type_list) {
  ttt <- training3[training3$classe==str,]

  tmp <- sample(c(1:(dim(ttt)[1])), min_sample, replace=FALSE)
  tmp2 <- ttt[tmp,]

  if(is.null(training4)) {
    training4 <- tmp2
  }else {
    training4 <- rbind(training4, tmp2)
  }
}

table(training4$classe)
```

# Prepare training data
```{r}
inTrain <- createDataPartition(y=training4$classe, p=0.7, list=FALSE)
m_train <- training4[inTrain,]
m_test  <- training4[-inTrain,]

table(m_train$classe)
table(m_test$classe)
```

## Training with lda
First try with simple classifier.
```{r}
modelLda <- train(classe ~., data=m_train, method="lda")
modelLda
```

But, the result of learning is poor. (69.1%)


## Training with rf
```{r}
modelRf <- train(classe ~., data=m_train, method="rf")
modelRf$finalModel

m_pred <- predict(modelRf$finalModel, newdata=m_test)
a <- cbind(m_test$classe, as.character(m_pred))
m_pred_tf <- ifelse(m_test$classe == as.character(m_pred), 1, 0)

accuracy <- table(m_pred_tf)[2]/sum(table(m_pred_tf))
accuracy

(1-accuracy)
```

99.3 %is acceptable.
So, I choose this model for this project.
